Finally Tagless, Partially Evaluated

### 2008-11-03 tagless/tagless-final.tex
Small fixes

The only interpreter in this paper that does not fit |Symantics1|
is the partial evaluator~|P|.  It does not fit because it uses
\emph{two} inductive maps on object types---both |'sv| and |'dv|
in Figure~\ref{fig:ocaml}.  We could define a |Symantics2|
signature to abstract over \emph{two} inductive maps over object
types; it would include 4 abstract types and 2 abstract type
constructors in addition to |repr|.  It would then be easy to
make~|P| match |Symantics2|, but the output of~|P| can still only
match |Symantics1|.  This escalation points to a need for either
record-kind polymorphism (so that |'dv| in
Figure~\ref{fig:inductive} may be more than just one type) or
type-indexed types (so that we do not need to emulate them in the
first place).

@@

Very recently others have also begun to realize the usefulness of being
able to abstract over higher-kinded types, like our |repr|.
\Citet{moors-generics-higher-kind} illustrate how they have leveraged the 
same power within Scala.  \Citet{HORM08} also uses Scala, yet are clearly
influenced by our work \citep{carette-kiselyov-shan-aplas}
(as they themselves note); where we have concentrated
on multiple efficient interpretations of the same language, they have 
concentrated on composability.

>>>>

The only interpreter in this paper that does not fit |Symantics1|
is the partial evaluator~|P|.  It does not fit because it uses
\emph{two} inductive maps on object types---both |'sv| and |'dv|
in Figure~\ref{fig:ocaml}.  We could define a |Symantics2|
signature to abstract over \emph{two} inductive maps over object
types; it would include 4 abstract types and 2 abstract type
constructors in addition to |repr|.  It would then be easy to
turn~|P| into a functor that returns a |Symantics2| module, but
the input to~|P| can still only
match |Symantics1|.  This escalation points to a need for either
record-kind polymorphism (so that |'dv| in
Figure~\ref{fig:inductive} may be more than just one type) or
type-indexed types (so that we do not need to emulate them in the
first place).

@@

Other researchers have very recently realized that it is useful to
abstract over higher-kinded types, like our |repr|.
\Citet{moors-generics-higher-kind} put the
same power to work in Scala.  \Citet{HORM08} also use Scala and note
that they are influenced by our work
\citep{carette-kiselyov-shan-aplas}.  Where we have concentrated
on multiple efficient interpretations of the same language, they have 
concentrated on composing the languages and interpretations.
